Figure 6 - networks

### 2024-08-08 ms_figure_6_networks.Rmd
minor edits to (S)Fig6

## Put together
figs6c <- cowplot::plot_grid(
    cowplot::plot_grid(
        tplot, 
        get_legend(ggeqn1, "right"), 
        similplot + theme(legend.position = "bottom"), 
        ggr150example + theme(legend.position = "none"), 
        align = "v", axis = "t", 
        labels = c("C", "", "", ""), nrow = 1, 
        rel_widths = c(1.1, 0.9, 1, 0.5)
    ),
    ggeqn2, ncol = 1, labels = "", 
    rel_heights = c(3, 1)
)
```

@@

```{r Fig6}
#| fig.width: 10
#| fig.height: 12
#| warning: false

fig6c <- ggdraw() + 
    draw_image("schematics/Fig6C_Pho7_protein_domains_cartoon_Arial_RGB.png")

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        pho7volc, 
        cowplot::plot_grid(
            cowplot::plot_grid(NULL, fig6c, NULL, nrow = 1,
                               rel_widths = c(0.25, 1, 0.1)),  
            ggrad_upset,
            ncol = 1, labels = c("B", "C"),
            rel_heights = c(1, 1.75)), 
        nrow = 1, labels = c("A", "")
    ),
    cowplot::plot_grid(
        cowplot::plot_grid(
            ggr150 + theme(legend.position = "none") + 
                ggtitle("150 mM NaCl IP-MS") + 
                theme(plot.title = element_text(hjust = 0.075, size = ft)), 
            ggr500 + theme(legend.position = "none") + 
                ggtitle("500 mM NaCl IP-MS") +
                theme(plot.title = element_text(hjust = 0.075, size = ft)), 
            nrow = 1, labels = c("D", "E")
        ),
        get_legend(ggr150 + theme(legend.position = "bottom"), "bottom"),
        nrow = 2, labels = c("", ""), rel_heights = c(1, 0.25)
    ),
    rel_heights = c(3.5, 5), 
    ncol = 1
)
```

>>>>

## Put together
figs6c <- cowplot::plot_grid(
    cowplot::plot_grid(
        tplot, 
        get_legend(ggeqn1, "right"), 
        similplot + theme(legend.position = "bottom"), 
        ggr150example + theme(legend.position = "none"), 
        align = "v", axis = "t", 
        labels = c("C", "", "", ""), nrow = 1, vjust = -0.5,
        rel_widths = c(1.1, 0.9, 1, 0.5)
    ),
    ggeqn2, ncol = 1, labels = "", 
    rel_heights = c(3, 1)
)
```

@@

```{r Fig6}
#| fig.width: 10
#| fig.height: 11
#| warning: false

fig6b <- ggdraw() + 
    draw_image("schematics/Fig6B_Pho7_protein_domains_cartoon_Arial_RGB.png")

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        pho7volc, 
        cowplot::plot_grid(
            cowplot::plot_grid(NULL, fig6b, NULL, nrow = 1,
                               rel_widths = c(0.25, 1, 0.1)),  
            ggrad_upset,
            ncol = 1, labels = c("B", "C"),
            rel_heights = c(1, 1.75)), 
        nrow = 1, labels = c("A", "")
    ),
    NULL,
    cowplot::plot_grid(
        cowplot::plot_grid(
            ggr150 + theme(legend.position = "none") + 
                ggtitle("150 mM NaCl IP-MS") + 
                theme(plot.title = element_text(hjust = 0.075, size = ft)), 
            ggr500 + theme(legend.position = "none") + 
                ggtitle("500 mM NaCl IP-MS") +
                theme(plot.title = element_text(hjust = 0.075, size = ft)), 
            nrow = 1, labels = c("D", "E"), vjust = 1.8
        ),
        get_legend(ggr150 + theme(legend.position = "bottom"), "bottom"),
        nrow = 2, labels = c("", ""), rel_heights = c(1, 0.1)
    ),
    rel_heights = c(3.5, 0.3, 4.25), 
    ncol = 1
)
```
